---
title: "Analysis sockult"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r cars}
library(tidyverse)
```

#-----DATA CLEANING------

#Importing dataframe and extracting all participants who finished as well as offer and response columns
```{r warning=FALSE, include=FALSE}

wide<-read.csv("data/all_apps_wide_2021-05-10.csv") #loading the wide dataframe with all data from oTree

df_wide<-filter(wide, wide$participant._current_page_name == "ThankYou")#filtering all participants who did not finish the experiment away. The last page in the experiment is called "ThankYou".
wide$participant.code<-as.factor(wide$participant.code)
df_wide<-df_wide[-c(1), ] 

Columns_offers<-grep(pattern="\\.Offer$", #Filtering the df_wide dataframe for all columns where participants give offers
    x=colnames(df_wide))

Columns_responds<-grep(pattern="\\.bot_side$", #Filtering the df_wide dataframe for all columns where bot responds
    x=colnames(df_wide))

Columns_description<-grep(pattern="\\.about_you$", #Filtering the df_wide dataframe for all columns where bot responds
    x=colnames(df_wide))

Persona_player<-grep(pattern="\\.P$", #Filtering the df_wide dataframe for all columns where bot responds
    x=colnames(df_wide))

OfferDf<- df_wide[, colnames(df_wide)[Columns_offers]] #A df with data from offers

ResponseDf<-df_wide[, colnames(df_wide)[Columns_responds]]  #A df with bot response

about_youDf<-df_wide[, colnames(df_wide)[Columns_description]]  #A df with the participants descriptions

```


-
#offer df
```{r include=FALSE}
#Extracting participant code, age and gender and adding them to the OfferDf
OfferDf["ParticipantCode"] <- df_wide$participant.code 
OfferDf["Age"] <- df_wide$Consentform.1.player.Age
OfferDf["Gender"] <- df_wide$Consentform.1.player.Gender

#relocating to the beginning of the dataframe
OfferDf <- OfferDf %>% 
  relocate(ParticipantCode, Age, Gender, .before =ultimatumn_anonym.1.player.Offer)

#renaming columns 
colnames(OfferDf) <- sub(".player.Offer", "", colnames(OfferDf))
colnames(OfferDf) <- sub("Persona", "P", colnames(OfferDf))
colnames(OfferDf) <- sub("ultimatumn_anonym", "An", colnames(OfferDf))
colnames(OfferDf) <- sub("An.1", "An1", colnames(OfferDf))
colnames(OfferDf) <- sub("An.2", "An1.2", colnames(OfferDf))
colnames(OfferDf) <- sub("An.3", "An1.3", colnames(OfferDf))
colnames(OfferDf) <- sub("An.4", "An1.4", colnames(OfferDf))
colnames(OfferDf) <- sub("An.5", "An1.5", colnames(OfferDf))
colnames(OfferDf) <- sub("An.6", "An1.6", colnames(OfferDf))
colnames(OfferDf) <- sub("An.7", "An1.7", colnames(OfferDf))
colnames(OfferDf) <- sub("An.8", "An1.8", colnames(OfferDf))
colnames(OfferDf) <- sub("An.9", "An1.9", colnames(OfferDf))
colnames(OfferDf) <- sub("An.10", "An10", colnames(OfferDf))
```


-
#response df
```{r include=FALSE}
#Doing the same
ResponseDf["ParticipantCode"] <- df_wide$participant.code 
ResponseDf["Age"] <- df_wide$Consentform.1.player.Age
ResponseDf["Gender"] <- df_wide$Consentform.1.player.Gender

colnames(ResponseDf) <- sub("ultimatumn_anonym", "An", colnames(ResponseDf))
colnames(ResponseDf) <- sub("player.bot_side", "Response", colnames(ResponseDf))
colnames(ResponseDf) <- sub("ultimatumn_anonym", "An", colnames(ResponseDf))
colnames(ResponseDf) <- sub("An.1", "An1", colnames(ResponseDf))
colnames(ResponseDf) <- sub("An.2", "An1.2", colnames(ResponseDf))
colnames(ResponseDf) <- sub("An.3", "An1.3", colnames(ResponseDf))
colnames(ResponseDf) <- sub("An.4", "An1.4", colnames(ResponseDf))
colnames(ResponseDf) <- sub("An.5", "An1.5", colnames(ResponseDf))
colnames(ResponseDf) <- sub("An.6", "An1.6", colnames(ResponseDf))
colnames(ResponseDf) <- sub("An.7", "An1.7", colnames(ResponseDf))
colnames(ResponseDf) <- sub("An.8", "An1.8", colnames(ResponseDf))
colnames(ResponseDf) <- sub("An.9", "An1.9", colnames(ResponseDf))
colnames(ResponseDf) <- sub("An.10", "An10", colnames(ResponseDf))
colnames(ResponseDf) <- sub("Persona", "P", colnames(ResponseDf))

ResponseDf <- ResponseDf %>% 
  relocate(ParticipantCode, Age, Gender, .before =An1.Response)
```

-
#Creating dataframe with responses and offers 
```{r include = FALSE}
#Combining responsedf and offerdf
Combined<-cbind(ResponseDf, OfferDf)

#including participants

Combined["ParticipantCode"] <- df_wide$participant.code 
Combined["Age"] <- df_wide$Consentform.1.player.Age
Combined["Gender"] <- df_wide$Consentform.1.player.Gende

#removing 
colnames(Combined ) <- sub(".player.Offer", "", colnames(Combined ))
colnames(Combined ) <- sub("Persona", "P", colnames(Combined ))
colnames(Combined) <- sub("player.bot_side", "Response", colnames(Combined))
colnames(Combined ) <- sub("ultimatumn_anonym", "An", colnames(Combined ))
colnames(Combined ) <- sub("An.1", "An1", colnames(Combined ))
colnames(Combined ) <- sub("An.2", "An1.2", colnames(Combined ))
colnames(Combined ) <- sub("An.3", "An1.3", colnames(Combined ))
colnames(Combined ) <- sub("An.4", "An1.4", colnames(Combined ))
colnames(Combined ) <- sub("An.5", "An1.5", colnames(Combined ))
colnames(Combined ) <- sub("An.6", "An1.6", colnames(Combined ))
colnames(Combined ) <- sub("An.7", "An1.7", colnames(Combined ))
colnames(Combined ) <- sub("An.8", "An1.8", colnames(Combined ))
colnames(Combined ) <- sub("An.9", "An1.9", colnames(Combined ))
colnames(Combined ) <- sub("An.10", "An10", colnames(Combined ))

Combined <- Combined %>% 
  relocate(Gender, .before =An1.Response)

```


-
#From wide to long format
```{r warning=FALSE, include=FALSE}
#from wide to long format for the Offer only df
df_long<-reshape(OfferDf, 
        direction = "long",
        varying = list(names(OfferDf)[4:83]),
        v.names = "Offer",
        idvar = c("ParticipantCode", "Age", "Gender"),
        timevar = "Round",
        times = c(names(OfferDf)[4:83]))

#Using a combined dataframe to convert response to long format
df_respons_long<-reshape(Combined, 
        direction = "long",
        varying = list(names(Combined)[4:83]),
        v.names = "Response",
        idvar =  "ParticipantCode",
        timevar = "Round",
        times = c(names(Combined)[4:83]))
```


-
#Creating Is_anonymous, OtherPlayer, PrevOffer, PrevResonse, centered_PrevOffer
```{r warning=FALSE}

df_long["Response"]<- df_respons_long$Response
df_long["Is_anonymous"] <- ifelse(grepl("An",df_long$Round),'1','0')

x<-rep(c(1,2,3,4,5,6,7,8),each=10) #addinf the "other" column for each person participants play against

#Creating the column "other"
df_long <- df_long %>% 
  group_by(ParticipantCode) %>% 
  mutate(Other = x)

pacman::p_load(tidyverse, ggpubr, groupdata2, lme4, lmerTest)

df_long["Response"]<- df_respons_long$Response #lagging response and offer
df_long <- df_long %>% 
  group_by(ParticipantCode, Other) %>% 
  mutate(PrevOffer = lag(Offer),
         PrevResponse =lag(Response))

#adding centered previous offer
df_long <- df_long %>% 
  group_by(ParticipantCode, Other) %>% 
  mutate(centered_PrevOffer = ( PrevOffer - 50))

#setting variables as factors
df_long$Gender<-as.factor(df_long$Gender)
df_long$ParticipantCode<-as.factor(df_long$ParticipantCode)

#write.csv(df_long,"/Users/annahedvigmoller/Desktop/df_long", row.names = TRUE)

```


-
#plots before analysis
```{r}
library()
#checking data, effect for gender and is anonymous
ggplot(df_long, aes(Offer)) + 
  geom_density() + 
  facet_wrap(~Is_anonymous) + 
  theme_minimal()

#log transforming offer to check if it gets better, it does not

df_long["log_offer"]<-log(df_long$Offer)

non_log<-ggplot(df_long, aes(Offer)) + 
  geom_density() + 
  scale_color_colorblind()+
  theme_minimal()

log<-ggplot(df_long, aes(log_offer)) + 
  geom_density() + 
  scale_color_colorblind()+
  theme_minimal()

log+non_log #comparing plots

#checking for ratio between accept or decline between personas
ggplot(df_long, aes(Response)) + 
  stat_count()+
  facet_wrap(~Other) + 
  theme_minimal()

```


#2. Predicting Offer based on anoynomus condition, gender, PrevResponse + random intercept for participantCode

 bf(Offer ~ 1 + Is_anonymous + Gender + PrevResponse + (1 |ParticipantCode))
 
#Mdodel2
```{r}

df_long["scaledOffer"]<-scale(df_long$Offer, scale = FALSE)

center_scale(df_long$Offer)

m1_PrevResponse1<- bf(Offer ~ 1 + Is_anonymous + Gender + PrevResponse + (1 |ParticipantCode))

get_prior(m1_PrevResponse1, data = df_long, family = gaussian) 

#setting priors

data_prior_m1_PrevResponse1 <- c(
  prior(normal(45,2), class = Intercept),
  prior(normal(-2,4), class = b, coef = GenderMale),
  prior(normal(0,6), class = b, coef = Is_anonymous1),
  prior(normal(0,4), class = b, coef = PrevResponseDecline),
  prior(normal(10,3), class = sd),
  prior(normal(12,2), class = sigma))

M2_PrevResponse1<-brm(
  m1_PrevResponse1,
  data=df_long,
  family= gaussian(),
  prior=data_prior_m1_PrevResponse1,
  sample_prior="only",
  chains = 2,
  cores = 2,
)
pp_m2_PrevResponse1<-pp_check(M2_PrevResponse1, nsamples = 100)
pp_m2_PrevResponse1

#Make first model, train on data with 4 chains

M2_PrevResponse_post1<-brm(
  m1_PrevResponse1,
  data=df_long,
  family= gaussian(),
  prior=data_prior_m1_PrevResponse1,
  sample_prior=T,
  chains = 4,
  cores = 2,
)

pp_m2_PrevResponsePost1<-pp_check(M2_PrevResponse_post1, nsamples = 100)
pp_m2_PrevResponse1+pp_m2_PrevResponsePost1


posterior_M2_PrevResponse1 <-  posterior_samples(M2_PrevResponse_post1) #sampling from posterior
warnings() #checking warnings

summary(M2_PrevResponse_post1)


```


#Chains trace check
```{r}
pacman::p_load(bayesplot,viridis,mice)
mcmc_rank_overlay(pp_m2_PrevResponsePost1, pars =  "b_PrevResponseDecline") + theme_classic()

mcmc_rank_overlay(pp_m2_PrevResponsePost1, pars =  "b_Is_anonymous1") + theme_classic()

mcmc_rank_overlay(pp_m2_PrevResponsePost1, pars = "b_GenderMale") + theme_classic()
```


-

#plots m2
```{r}
##prevresponseDecline
m2_PrevResponseDecline<- ggplot(pp_m2_PrevResponsePost1) +
  theme_classic() +
  geom_density(aes(prior_b_PrevResponseDecline), fill="red", alpha=0.3) +
  geom_density(aes(b_PrevResponseDecline), fill="blue", alpha=0.5)


## anonymous
m2_Is_anonymous1<- ggplot(pp_m2_PrevResponsePost1) +
  theme_classic() +
  geom_density(aes(prior_b_Is_anonymous1), fill="red", alpha=0.3) +
  geom_density(aes(b_Is_anonymous1), fill="blue", alpha=0.5)


## gender
m2_Gender2<- ggplot(pp_m2_PrevResponsePost1) +
  theme_classic() +
  geom_density(aes(prior_b_GenderMale), fill="red", alpha=0.3) +
  geom_density(aes(b_GenderMale), fill="blue", alpha=0.5)


m2_PrevResponseDecline+m2_Is_anonymous1+m2_Gender2

#Participantcode
m2_ParticipantCode<- ggplot(pp_m2_PrevResponsePost1) +
  theme_classic() +
  geom_density(aes(prior_sd_ParticipantCode), fill="red", alpha=0.3) +
  geom_density(aes(sd_ParticipantCode__Intercept), fill="blue", alpha=0.5)
m2_ParticipantCode
#sigma
m2_sigma<- ggplot(pp_m2_PrevResponsePost1) +
  theme_classic() +
  geom_density(aes(prior_sigma), fill="red", alpha=0.3) +
  geom_density(aes(sigma), fill="blue", alpha=0.5)
m2_sigma

#intercept
m2_Intercept<- ggplot(pp_m2_PrevResponsePost1) +
  theme_classic() +
  geom_density(aes(prior_Intercept), fill="red", alpha=0.3) +
  geom_density(aes(b_Intercept), fill="blue", alpha=0.5)


m2_Intercept+m2_sigma+m2_ParticipantCode

```


-
#conditional effects
```{r}
plot(conditional_effects(M2_PrevResponse_post1, spaghetti=T, nsamples=100, method = "fitted"), points=F)

plot(conditional_effects(pp_m2_PrevResponsePost1, spaghetti=T, nsamples=100, method = "predict"), points=F)

```

#hypothesis testing
```{r}

summary(M2_PrevResponse_post1)
hypothesis(M2_PrevResponse_post1, "Is_anonymous1  < 0") 
plot(hypothesis(M2_PrevResponse_post1, "Is_anonymous1  < 0"))

hypothesis(M2_PrevResponse_post1, "GenderMale  < 0") 
plot(hypothesis(M2_PrevResponse_post, "GenderMale  < 0")  )

hypothesis(M2_PrevResponse_post1, "Is_anonymous1 - GenderMale< 0") 
plot(hypothesis(M2_PrevResponse_post1, "Is_anonymous1 < 0"))

hypothesis(M2_PrevResponse_post1, "PrevResponseDecline  < 0") 
plot(hypothesis(M2_PrevResponse_post, "PrevResponseDecline  < 0"))

```







#---Persona Semantic Preprocessing-----

#Making Persona dataframes with one word in each row
```{r include=FALSE}
library(dplyr)
library(tidytext)


library(data.table)
load("EN_100k_lsa.rda")
EN100k<-as.data.frame(EN_100k_lsa)

setDT(EN100k, keep.rownames = TRUE)[]

Persona_df <- data.frame (Descriptions = c('I am a 24 year old woman and I study international business communication in Spanish on 5th semester at bachelor’s level. In my spare time I’m active in a political youth party and I like going on long walks with my friends from my studies and the party. During corona I have been baking sourdough bread and started going for walks.','Work as a personal consultant in Danske bank guiding clients with investments. When I’m off work, I am together with my fiancé and kids. I golf and ride mountain bike with my coworkers in the weekends/off-work days','My name is Camilla and I’m 19 years old. Im in 3.G in Gymnasium and become a student in June. After the summer i want to study a bachelor in law at Aalborg university and move there with my two friends from my gymnasium. In my spare time i read a lot and watch some Netflix shows.','I am 23 years old and work part time in Bilka in the garden department. I like taking rides on my motorcycle. I enjoy gardening, cooking and spending time with my friends and play with my cat. I am trying to get a job as an environmental technologist. I am not doing much during these times, looking forward to an open world again so I can travel.','I’m 21 years old and a student.I study datascience and I have a student-job at a printer firm. In my free time I 
play piano, paint and read books. I also enjoy watching YouTube and I spend way too much time on Twitter'),
Persona=c("Persona_1","Persona_2","Persona_3","Persona_4","Persona_5"))

#running the first participant through the sentiment analysis in order to rowbind the following participants to the dataframe
text<-c(Persona_df$Descriptions[1]) 
persona_about_you_word<-data.frame(text) %>% unnest_tokens(word, text)

sentiment_persona<-filter(EN100k, rn %in% persona_about_you_word$word) %>% 
  mutate(Persona = Persona_df$Persona[1]) %>% 
  relocate(Persona, .before = rn)  %>% 
  rename(word = rn)

#loop through each participant and adding their sentiment scores
for (row_nr in 2:nrow(Persona_df)){
  
  text<-c(Persona_df$Descriptions[row_nr])
  
  about_you_word<-data.frame(text) %>% unnest_tokens(word, text)
  
  temporary_sentiment<-filter(EN100k, rn %in% about_you_word$word) %>% 
    
  mutate(Persona = Persona_df$Persona[row_nr]) %>% 
  relocate(Persona, .before = rn)  %>% 
  rename(word = rn)
  
  sentiment_persona<-rbind(sentiment_persona, temporary_sentiment)
}

sentiment_persona<-as.data.frame(sentiment_persona)  #setting it as dataframe
mean <- aggregate(sentiment_persona[,3:302], list(sentiment_persona$Persona), FUN = mean) #taking average of each semantic dimension across words for each participant

mean_persona<-mean %>% rename(Persona =Group.1)

```

-
#merging EN_100K with about you for participants
```{r}


class(df_wide$participant.code)

df_wide$participant.code<-as.factor(df_wide$participant.code)
about_youDf<-data.frame(about_youDf)

about_youDf["ParticipantCode"]<- df_wide$participant.code #adding participant code
View(about_youDf)

#running the first participant through the sentiment analysis in order to rowbind the following participants to the dataframe
text_participants<-c(about_youDf$about_youDf[1]) 
about_you_word<-data.frame(text) %>% unnest_tokens(word, text)

sentiment<-filter(EN100k, rn %in% about_you_word$word) %>% 
  mutate(PartcipantCode = about_youDf$ParticipantCode[1]) %>% 
  relocate(PartcipantCode, .before = rn)  %>% 
  rename(word = rn)

#loop through each participant and adding their sentiment scores
for (row_nr in 2:nrow(about_youDf)){
  
  text<-c(about_youDf$about_youDf[row_nr])
  
  about_you_word<-data.frame(text) %>% unnest_tokens(word, text)
  
  temporary_sentiment<-filter(EN100k, rn %in% about_you_word$word) %>% 
    
  mutate(PartcipantCode = about_youDf$ParticipantCode[row_nr]) %>% 
  relocate(PartcipantCode, .before = rn)  %>% 
  rename(word = rn)
  
  sentiment<-rbind(sentiment, temporary_sentiment)
}

sentiment<-as.data.frame(sentiment)  #setting it as dataframe
mean <- aggregate(sentiment[,3:302], list(sentiment$PartcipantCode), FUN = mean) #taking average of each semantic dimension across words for each participant

mean<-mean %>% rename(ParticipantCode =Group.1)

new_dataset<-read_csv("Cosine-similaritydf.csv")


```


```{r}
library(pacman)
#install.packages("SnowballC")
#install.packages("lsa")
library(lsa)

```
-
#persona1

```{r}
#Trying to calculate 1 semantic distance:

mean_persona_V<-mean_persona[,2:301]

mean_participant_V<-mean[,2:301]

vec1<-c(as.vector(mean_participant_V[1,1:300]))
vec1<- as.numeric(unlist(vec1))

vec2<-c(as.vector(mean_persona_V[1,1:300]))
vec2<- as.numeric(unlist(vec2))

cos_similarity<-cosine(vec1,vec2)
cos_similarity
cos_similarity<-as.data.frame(cos_similarity)

#for persona 1:
for (row_nr in 2:nrow(mean_participant_V)){
  
  vec1<-c(as.vector(mean_participant_V[row_nr,1:300]))
  vec1<- as.numeric(unlist(vec1))
  
  vec2<-c(as.vector(mean_persona_V[1,1:300]))
  vec2<- as.numeric(unlist(vec2))

  cos_sim<-cosine(vec1,vec2)
  
  cos_similarity<-rbind(cos_similarity, cos_sim)
}

cos_similarity["ParticipantCode"]<- df_wide$participant.code #binding participant to the df
```

-
#Persona2
```{r}
#Trying to calculate 1 semantic distance:

vec2<-c(as.vector(mean_participant_V[1,1:300]))
vec2<- as.numeric(unlist(vec2))

vec3<-c(as.vector(mean_persona_V[2,1:300]))
vec3<- as.numeric(unlist(vec3))

cos_similarity_Persona2<-cosine(vec2,vec3)

cos_similarity_Persona2<-as.data.frame(cos_similarity_Persona2)

#for persona 2:
for (row_nr in 2:nrow(mean_participant_V)){
  
  vec1<-c(as.vector(mean_participant_V[row_nr,1:300]))
  vec1<- as.numeric(unlist(vec1))
  
  vec2<-c(as.vector(mean_persona_V[2,1:300]))
  vec2<- as.numeric(unlist(vec2))

  cos_sim<-cosine(vec1,vec2)
  
  cos_similarity_Persona2<-rbind(cos_similarity_Persona2, cos_sim)
}

cos_similarity_Persona2["ParticipantCode"]<- df_wide$participant.code #binding participant to the df
```



-
#Persona3
```{r}
#Trying to calculate 1 semantic distance:

vec3<-c(as.vector(mean_participant_V[1,1:300]))
vec3<- as.numeric(unlist(vec3))

vec4<-c(as.vector(mean_persona_V[3,1:300]))
vec4<- as.numeric(unlist(vec4))

cos_similarity_Persona3<-cosine(vec3,vec4)

cos_similarity_Persona3<-as.data.frame(cos_similarity_Persona3)

#for persona 3:
for (row_nr in 2:nrow(mean_participant_V)){
  
  vec1<-c(as.vector(mean_participant_V[row_nr,1:300]))
  vec1<- as.numeric(unlist(vec1))
  
  vec2<-c(as.vector(mean_persona_V[3,1:300]))
  vec2<- as.numeric(unlist(vec2))

  cos_sim<-cosine(vec1,vec2)
  
  cos_similarity_Persona3<-rbind(cos_similarity_Persona3, cos_sim)
}

cos_similarity_Persona3["ParticipantCode"]<- df_wide$participant.code #binding participant to the df
```


-
#Persona4
```{r}
#Trying to calculate 1 semantic distance:

vec4<-c(as.vector(mean_participant_V[1,1:300]))
vec4<- as.numeric(unlist(vec4))

vec5<-c(as.vector(mean_persona_V[4,1:300]))
vec5<- as.numeric(unlist(vec5))

cos_similarity_Persona4<-cosine(vec4,vec5)

cos_similarity_Persona4<-as.data.frame(cos_similarity_Persona4)

#for persona 4:
for (row_nr in 2:nrow(mean_participant_V)){
  
  vec1<-c(as.vector(mean_participant_V[row_nr,1:300]))
  vec1<- as.numeric(unlist(vec1))
  
  vec2<-c(as.vector(mean_persona_V[4,1:300]))
  vec2<- as.numeric(unlist(vec2))

  cos_sim<-cosine(vec1,vec2)
  
  cos_similarity_Persona4<-rbind(cos_similarity_Persona4, cos_sim)
}

cos_similarity_Persona4["ParticipantCode"]<- df_wide$participant.code #binding participant to the df
```

-
#Persona5
```{r}
#Trying to calculate 1 semantic distance:

vec4<-c(as.vector(mean_participant_V[1,1:300]))
vec4<- as.numeric(unlist(vec4))

vec5<-c(as.vector(mean_persona_V[5,1:300]))
vec5<- as.numeric(unlist(vec5))

cos_similarity_Persona5<-cosine(vec4,vec5)

cos_similarity_Persona5<-as.data.frame(cos_similarity_Persona5)

#for persona 5:
for (row_nr in 2:nrow(mean_participant_V)){
  
  vec1<-c(as.vector(mean_participant_V[row_nr,1:300]))
  vec1<- as.numeric(unlist(vec1))
  
  vec2<-c(as.vector(mean_persona_V[5,1:300]))
  vec2<- as.numeric(unlist(vec2))

  cos_sim<-cosine(vec1,vec2)
  
  cos_similarity_Persona5<-rbind(cos_similarity_Persona5, cos_sim)
}

cos_similarity_Persona5["ParticipantCode"]<- df_wide$participant.code #binding participant to the df
```

-
#Merging all 5 dataframes together
```{r}

Cosine_similarity_df<-rbind(cos_similarity,cos_similarity_Persona2,cos_similarity_Persona3,cos_similarity_Persona4,cos_similarity_Persona5)

```


-
#Filtering The df_long to only contain non-anonymous condition:
```{r}
library(tidyverse)
library(dplyr)

filteredForNA<-filter(df_long, Is_anonymous == 0)
filteredForNA$Round<-as.factor(filteredForNA$Round)

x<-rep(c(4,5,6,7,8),each= 26)

Cosine_similarity_df <- Cosine_similarity_df %>% 
  mutate(Other = x)

new_dataset <- filteredForNA %>% right_join(Cosine_similarity_df, by=c("ParticipantCode","Other"))   %>% rename(
    Semantic_distance = V1
    )

  
#write.csv(new_dataset,"/Users/annahedvigmoller/Elgiganten Cloud/Uni/4. Semester/Social cultural #dynamics/sockult_exam_new/Aanlysis/Cosine-similaritydf.csv", row.names = TRUE)

```






#2.2 Cosine similarity

#model 1
Offer_BigModel<- bf(Offer ~ 1 + Scaled_sem + Gender + PrevResponse + (1 |ParticipantCode)) 
```{r}

new_dataset["Scaled_sem"]<-scale(new_dataset$Semantic_distance)

new_dataset$Gender<-as.factor(new_dataset$Gender)
new_dataset$ParticipantCode<-as.factor(new_dataset$ParticipantCode)

Offer_BigModel<- bf(Offer ~ 1 + Scaled_sem + PrevResponse + Gender + (1 |ParticipantCode)) 

get_prior(Offer_BigModel, data = 
new_dataset, family = gaussian) 

mean(new_dataset$Offer)
sd(new_dataset$Offer)
hist(new_dataset$Offer)
#setting priors

Offer_BigModel_prior <- c(
  prior(normal(45,4), class = Intercept), 
  prior(normal(-2,4), class = b, coef = GenderMale), 
  prior(normal(0,4), class = b, coef = PrevResponseDecline), 
  prior(normal(3,2), class = b, coef = Scaled_sem),
  prior(normal(12,3), class = sd),
  prior(normal(12,2), class = sigma))

#running model with prior 
Prior_Offer_BigModel<-brm(
  Offer_BigModel,
  data=new_dataset,
  family= gaussian(),
  prior=Offer_BigModel_prior,
  sample_prior="only",
  chains = 2,
  cores = 2,
)


pp_Offer_BigModel<-pp_check(Prior_Offer_BigModel, nsamples = 100)

pp_Offer_BigModel

#Training the model on data with 4 chains
Post_Offer_BigModel<-brm(
  Offer_BigModel,
  data=new_dataset,
  family= gaussian(),
  prior=Offer_BigModel_prior,
  sample_prior=T,
  chains = 4,
  cores = 2,
)

pp_Offer_BigModelpost<-pp_check(Post_Offer_BigModel, nsamples = 100)

pp_Offer_BigModel+pp_Offer_BigModelpost

ggplot(new_dataset, aes(x=Scaled_sem, y= Offer)) + geom_density()

ggplot(new_dataset,aes(x=Scaled_sem, y=Offer)) + geom_point()


summary(Post_Offer_BigModel)
Post_Offer_BigModel_posterior<-  posterior_samples(Post_Offer_BigModel)
hypothesis(Post_Offer_BigModel, "Scaled_sem > 0")
```
-
-
#checking chains
```{r}
mcmc_rank_overlay(Post_Offer_BigModel, pars = "b_Intercept", "b_Scaled_sem") + theme_classic()

mcmc_rank_overlay(Post_Offer_BigModel, pars = "b_Intercept","b_GenderMale") + theme_classic()

mcmc_rank_overlay(Post_Offer_BigModel, pars = "b_Intercept","b_PrevResponseDecline") + theme_classic()
citation()
```

-
#plots
```{r}
p1_prevResponse2<- ggplot(Post_Offer_BigModel_posterior) +
  theme_classic() +
  geom_density(aes(prior_b_PrevResponseDecline), fill="red", alpha=0.3) +
  geom_density(aes(b_PrevResponseDecline), fill="blue", alpha=0.5)
p1_prevResponse

## gender
p2_prevResponse<- ggplot(Post_Offer_BigModel_posterior) +
  theme_classic() +
  geom_density(aes(prior_b_GenderMale), fill="red", alpha=0.3) +
  geom_density(aes(b_GenderMale), fill="blue", alpha=0.5)

p2_prevResponse


p1_prevResponse+p2_prevResponse+p1.2

p1.2<- ggplot(Post_Offer_BigModel_posterior) +
  theme_classic() +
  geom_density(aes(prior_b_Scaled_sem), fill="red", alpha=0.3) +
  geom_density(aes(b_Scaled_sem), fill="blue", alpha=0.5)
p1.2

## gender
p3.2<- ggplot(Post_Offer_BigModel_posterior) +
  theme_classic() +
  geom_density(aes(prior_b_Gender2), fill="red", alpha=0.3) +
  geom_density(aes(b_Gender2), fill="blue", alpha=0.5)

p3.2

p1.2+p3.2+p1_prevResponse

p2<- ggplot(Post_Offer_BigModel_posterior) +
  theme_classic() +
  geom_density(aes(prior_sd_ParticipantCode), fill="red", alpha=0.3) +
  geom_density(aes(sd_ParticipantCode__Intercept), fill="blue", alpha=0.5)
p2

p3<- ggplot(Post_Offer_BigModel_posterior) +
  theme_classic() +
  geom_density(aes(prior_sigma), fill="red", alpha=0.3) +
  geom_density(aes(sigma), fill="blue", alpha=0.5)
p3

p4<- ggplot(Post_Offer_BigModel_posterior) +
  theme_classic() +
  geom_density(aes(prior_Intercept), fill="red", alpha=0.3) +
  geom_density(aes(b_Intercept), fill="blue", alpha=0.5)
p4

p3+p4+p2
```



#checking conditional effects
```{r}
plot(conditional_effects(Post_Offer_BigModel, spaghetti=T,nsamples=100, method ="predict"), points=T)
plot(conditional_effects(Post_Offer_BigModel, spaghetti=T,nsamples=100, method ="fitted"), points=F)
```

#hyp testing
```{r}
summary(Post_Offer_BigModel)
hypothesis(Post_Offer_BigModel, " Scaled_sem > 0") 
plot(hypothesis(Post_Offer_BigModel, "Scaled_sem  < 0"))

hypothesis(Post_Offer_BigModel, " Scaled_sem + GenderMale > 0") 
plot(hypothesis(Post_Offer_BigModel, "Scaled_sem + GenderMale  < 0"))

hypothesis(Post_Offer_BigModel, "GenderMale  < 0") 
plot(hypothesis(Post_Offer_BigModel, "GenderMale  < 0")  )

hypothesis(Post_Offer_BigModel, "PrevResponseDecline  < 0") 
plot(hypothesis(Post_Offer_BigModel, "PrevResponseDecline  < 0"))
```




